From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-18 paper.tex
Minor changes

Please refer to~\cite{Hood:2015} for the implementation of the hand-writing
activity.

@@

\subsubsection{From Face Detection to Focus of Attention} \label{fromFaceTo}
(note that the focus of attention
was separately hand-coded, {\it post-hoc}, from the video recording of the
interaction).

>>>>

The implementation of the hand-writing activity itself has been previously
presented in~\cite{Hood:2015}.

@@

We performed a {\it post-hoc} coding the video records to manually of the
interaction were (note that the focus of attention was separately hand-coded,
{\it post-hoc}, from the video recording of the interaction).

\subsubsection{From Face Detection to Focus of Attention} \label{fromFaceTo}
